Smoothing seismicity techniques applied to seismic sources characterization and probabilistic seismic hazard analysis in Brazil

### 2014-10-02 manuscript.tex
1st steps... title, author, affiliation, etc...

\documentclass[draft,jgrga]{AGUTeX}

@@

% Author names in capital letters:
\authorrunninghead{ASSUMPCAO M.}

@@

% Shorter version of title entered in capital letters:
\titlerunninghead{SHORT TITLE}

@@

% Corresponding author mailing address and e-mail address:
\authoraddr{Corresponding author: Jane Smith, Department of Geography, Ohio State University, Columbus, Ohio, USA. (j.smith@ohio.edu)}

@@

\title{manuscript agu}

@@

\authors{John Smith,\altaffilmark{1}
James Smith,\altaffilmark{1,2}, and
Jane Smith\altaffilmark{2}}

\altaffiltext{1}{Department of Hydrology and Water Resources, University of Arizona, Tucson, Arizona, USA.}

\altaffiltext{2}{Department of Geography, Ohio State University, Columbus, Ohio, USA.}

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed vehicula metus sapien. Suspendisse pulvinar, felis ut hendrerit aliquet, dui nisi bibendum erat, fermentum mattis enim nibh id arcu. Vestibulum ultrices eros sed odio tincidunt bibendum. Pellentesque fermentum ante vel nulla commodo fermentum. Vestibulum in augue sit amet libero viverra accumsan eu at magna. Sed at ligula quis nibh pharetra facilisis non eu libero. Suspendisse non quam sit amet massa luctus interdum sit amet in purus. Integer id orci elit, vitae sollicitudin lectus.

>>>>

\documentclass[draft,grl]{AGUTeX}

@@

% Author names in capital letters:
\authorrunninghead{PIRCHINER M.}

@@

% Shorter version of title entered in capital letters:
\titlerunninghead{Brazilian Smoothing Seismicity and PSHA}

@@

% Corresponding author mailing address and e-mail address:
\authoraddr{Corresponding author: Marlon Pirchiner, Department of Geophysics, IAG, USP, São Paulo, Brazil.
(marlon.pirchiner@iag.usp.br)}

@@

\title{Smoothing seismicity techniques applied to 
seismic sources characterization and 
probabilistic seismic hazard analysis in Brazil}

@@

\authors{Marlon Pirchiner\altaffilmark{1,2}}

\altaffiltext{1}{Department of Geophysics, 
Institute of Astronomy, Geophysics and Atmospherical Sciences, 
University of São Paulo, São Paulo, Brazil.}

\altaffiltext{2}{School of Applied Math, Getúlio Vargas Foundation, Rio de Janeiro, Brazil.}

@@

abrastcasrtasdlkjh alksjd flkajhsd flkjahds flkjahsdlkfja slkdjfh alskjdfh laksjdhf lakjshdfl ajhds lfkja lksdjflaksjdf
lakjsf akjshdfl akjdsfljkahds lfkjahds lkjahsdlfkjas ldkjfh laskjdhf laksjf lasdfh
asdflkajf lkajshdf lajshdfliuhp 9qerjhtgnv.k, zmxcnpq;awe. ksmdnf va.,fxcnvpq ;.jars,mndf vq;asgdv
qolehfbd nvqlas,dbnv qalsd.vjhbq oalsk.ezjrbnfc;wq asdl.Zxgjyvqehratnpg oq;ve.krasj gbeq;adr.fxngb
